Keyword and Collocation analysis on India-related text of Natural History

### 2023-06-14 paper_quarto.qmd
0614 update

@@

```{r}
# build frequency list for target corpus
flist_target <- fnames_indiatext %>%
  freqlist(re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
           file_encoding     = "windows-1252") %>%
  print()
# build frequency list for reference corpus
flist_ref <- fnames_wholetext %>%
  freqlist(re_token_splitter = r"--[(?xi)  \s+   ]--",
           file_encoding     = "windows-1252") %>%
  print()
```

```{r}
flist_target %>% 
  as_tibble() %>% 
  kbl(col.names = c("Rank", "Type", "Absolute", "Relative")) %>% 
  kable_minimal(full_width = FALSE) %>% 
  add_header_above(c(" " = 2, "Frequency" = 2)) %>% 
  scroll_box(height = "400px")
```

@@

>>>>

```{r}
library(ggplot2)
library(dplyr)

data <- read.csv("geotext_whole.csv")

summary_data <- data %>%
  group_by(ToposText_ID, Place_Name) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  top_n(30, Count) %>% print()

```

```{r}
ggplot(summary_data, aes(x = Count, y = reorder(Place_Name, Count))) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(x = "Count", y = "Place_Name") +
  ggtitle("Top 30 Most Referred Location Names") +
  facet_wrap(~ Place_Name, ncol = 1, scales = "free_y") +
  theme(axis.text.y = element_text(size = 8, hjust = 0.5))
```

@@

```{r}
# build frequency list for target corpus
flist_target <- fnames_indiatext %>%
  freqlist(
    re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
    re_token_transf_in = "[[:punct:]]", # Match punctuation marks
    token_transf_out = "" # Replace punctuation marks with an empty string
  ) %>%
  print()

# build frequency list for reference corpus
flist_ref <- fnames_wholetext %>%
  freqlist(re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
           re_token_transf_in = "[[:punct:]]", # Match punctuation marks
           token_transf_out = "") %>%
  print()

# calculate scores
scores_kw <- assoc_scores(flist_target, flist_ref)

top_scores_kw <- scores_kw %>% 
  filter(PMI >= 2 & G_signed >= 2)

# print top_scores_kw, sorted by PMI
top_scores_kw %>%
  print(sort_order = "PMI")

# print top_scores_kw, sorted by G_signed
top_scores_kw %>%
  print(sort_order = "G_signed")
```

```{r}
top_scores_kw %>% # also valid for top_scores_colloc
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(PMI)) %>%             # sort by PMI (descending) 
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")
```

@@

```{r}
coocs <- fnames_wholetext %>% 
  surf_cooc("(?xi)  ^ india $", 
            re_token_splitter = r"--[(?xi)    \s+   ]--", # whitespace as token splitter
            re_token_transf_in = "[[:punct:]]", # Match punctuation marks
            token_transf_out = "")
coocs$target_freqlist
coocs$ref_freqlist

# calculate scores
scores_colloc <- assoc_scores(coocs)

top_scores_colloc <- scores_colloc %>% 
  filter(PMI >= 2 & G_signed >= 2)

# print top_scores_colloc, sorted by PMI
top_scores_colloc %>%
  print(sort_order = "PMI")

# print top_scores_colloc, sorted by G_signed
top_scores_colloc %>%
  print(sort_order = "G_signed")
```

```{r}
top_scores_colloc %>% # also valid for top_scores_kw
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>% # select 4 columns
  arrange(desc(G_signed)) %>%        # sort by G_signed (descending)  
  head(30) %>%                       # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")
```
